\tool: Revisiting BadUSB with Type-C

### 2021-01-30 WOOT/Files/experiment.tex
edits, not done.

\section{Experiment}
\label{sec:experiment}
\shuqing{Many parts in this section are much more likely to lie in implementation, introducing how \tool works. Doesn't look like experiment.}

%\shuqing{Experiment for devices and case study needed.}
To evaluate the effectiveness of \tool in different modes, we conducted three
experiments on \tool using devices with USB Type-C capabilities from different
OEMs, including a mobile phone, a tablet, and a laptop.

\textit{Setup.} \fengwei{I would suggest to add references for devices such as
Pi, ATMEGA32U4 board, Yamazawa, etc.} As mentioned in Section~\ref{sec:badusb},
our \tool only requires common components that are easily accessible online or
in any electronic store. Here we choose the following parts to build a
prototype. To begin with, we choose the Raspberry Pi 4B~\cite{pi4b} as the embedded
computer inside \tool, which is powerful enough to process video data and has
an onboard WiFi chip. As for the HID emulator, we decide to use an ATMEGA32U4 board~\cite{atmel}
with USB protocol support. This Atmel chip is able to emulate most HID devices
with our modified firmware. About the USB 3.x hub, we use one from the
UGREEN~\cite{ugreen}, which supports HDMI, USB 2.0, and many other exported peripheral.
Apart from these essential parts, we also use an auxiliary power-bank to
provide power for the Raspberry Pi and the mobile devices used by the victim.
The image of our prototype \tool can be found in Figure~\ref{fig:armory}.
\fengwei{We need to explain the Figure. What is "A"? What is "B", Where are 1,
2, 3, 4, and 5?}\hongyi{Is the caption sufficient? If explain here, I feel quite redundant}

>>>>

\section{Experiment}
\label{sec:experiment}
%\shuqing{Many parts in this section are much more likely to lie in implementation, introducing how \tool works. Doesn't look like experiment.}

%\shuqing{Experiment for devices and case study needed.}

To evaluate the effectiveness of \tool in different modes, we conducted three
experiments on \tool using devices with USB Type-C capabilities from different
OEMs, including a mobile phone, a tablet, and a laptop.

\textit{Setup.} 
%\fengwei{I would suggest to add references for devices such as
%Pi, ATMEGA32U4 board, Yamazawa, etc.} 
As mentioned in Section~\ref{sec:badusb},
our \tool only requires common components that are easily accessible online or
in any electronic store. Here we choose the following parts to build a
prototype. To begin with, we choose the Raspberry Pi 4B~\cite{pi4b} as the embedded Single Board 
Computer inside \tool, which is powerful enough to process video data and has
an onboard WiFi chip. As for the HID Emulator, we use an Atmel ATMEGA32U4 board~\cite{atmel}
with USB protocol support, which is able to emulate multiple HID devices
with our modified firmware. About the USB 3.x Hub, we use one from the
UGREEN~\cite{ugreen}, which supports HDMI, USB 2.0, and many other exported peripherals.
Apart from these essential parts, we also use an auxiliary power-bank to
provide power for the Raspberry Pi and the mobile devices used by the victim.
The image of our prototype \tool can be found in Figure~\ref{fig:armory}.
\mycircled{A} is a Huawei mobile phone as the victim's device; \mycircled{B} is a compact look of \tool prototype; \mycircled{1} is the USB 3.x Hub; \mycircled{2} is a Raspberry Pi 4B as the Single Board Computer; \mycircled{3} is an auxiliary power bank; \mycircled{4} is the Video Capture Card; \mycircled{5} is Atmel ATMEGA32U4 board as the HID Emulator. 
%\fengwei{We need to explain the Figure. What is "A"? What is "B", Where are 1,
%2, 3, 4, and 5?}\hongyi{Is the caption sufficient? If explain here, I feel quite redundant}
\fengwei{I think it is necessary to explain them in the text again.}
